### 2024-03-21 paper/content.tex
Incorporate reviewer comments

\item \textbf{Applicability to real-world scenarios:}
The third model contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations clustered around two stable directions.
The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.

@@

\subsection{Applicability to real-world scenarios}

This test represents a more complex scenario by simulating 103 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$.
The synthetic $b_z$ data were generated on a regular grid with $\qty{2}{\um}$ spacing and $\qty{5}{\um}$ sensor-sample distance.
We contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and $\qty{50}{\nano\tesla}$ standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.

@@

In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted a test of our algorithm on multiple synthetic datasets with increasing concentrations of randomly distributed magnetic grains. For each concentration, we generated 15 different random grain distributions. Figure~\ref{grain-concentration}a depicts the percentage of particles detected by the algorithm, with the median of the distribution represented by the red line. The same figure also presents the percentage of particles whose inversion results meet the filtering criteria of $R^2 \geq 0.85$ and $\text{SNR} \geq 5$, with the median represented by the blue line. As the number of particles increases, there is a consistent decrease in the percentage of sources detected. This is expected because of the spatial constraints of the algorithm, which require magnetic sources to be spatially separated for the detection algorithm to identify them. As shown in Figure~\ref{grain-concentration}b, by calculating the angular misfit between the vector sum direction of the model and the vector sum direction of the detected windows, it is observed that, for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains. Nonetheless, this angular misfit tends to approach zero when the filtering criteria are applied, regardless of the particle concentration.

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/grain-concentration.png}
  \caption{ 
  Different grain simulations were randomly replicated (N=15) to assess the effectiveness of the algorithm to detect the magnetic sources. a) The efficacy of the detection was measured by the percentage of sources identified ($100 \left( N_{detected} ~/~ N_{true} \right)$) and showed as box-plots for both unfiltered detection (median represented as the red line) and filtered detection ($R^2 \geq 0.85$ and $SNR \geq 5$, blue line). b) The same representation is displayed for the angular misfit between the true vector sum and both results for the filtered and unfiltered sum of vectors detected. The blue/red dots represent outliers in the distributions.
  }
  \label{grain-concentration}
\end{figure}

@@

We developed an efficient semi-automated method to determine the direction of magnetization of dipolar sources on a microscale, as well as the estimate of their magnetic moment.
It is ideal for a reinterpretation for the application of methods of paleomagnetic studies using thin sections of rock samples.
This would be an attempt to improve the quality of results obtained by isolating the responses of more reliable recorders of the Earth's geomagnetic field.

We also present a new way to solve the Euler deconvolution problem for determining the position of magnetic anomaly sources. Instead of the traditional moving window approach, we select data windows based on the Laplacian of Gaussian method applied to total gradient amplitude maps.
In this way, each window will ideally contain a single source and we are able to reduce the usually numerous spurious solutions to just a single solution per source.
This approach could also be adapted for traditional aeromagnetic data studies in cases where the sources are approximately spherical or only slightly elongated.

@@

The test using a simple synthetic sample shows the great capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity for both dipolar and non-dipolar sources, even under the effect of high-frequency noise.
The complex synthetic sample data allows observing the applicability of the method developed in real samples that are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
The real data application positively answered the question of the algorithm's ability to deal with the real-world signals of thin sections of rocks.
It also showed the acceptable capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal intensity disparities that were even greater than simulated in the complex synthetic test.
We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).

We expect that this method can be widely applied to magnetic microscopy studies involving particles in the SD and PSD domains. The method can be applied in full as presented here or its individual components (source detection, Euler deconvolution, dipole moment inversion) can be combined with existing or future methods. There are still issues to be overcome with regard to situations where the signal of two or more sources overlap significantly, when non-dipolar effects are strong even at larger source-sensor separations, and how to best combine and benchmark the inversion results against microCT and micromagnetic modeling studies.

>>>>

\item \textbf{Applicability to more complex scenarios:}
The third model is inspired on typical speleothem datasets.
It contains 103 dipoles with different dipole moment magnitudes, having inclinations and declinations clustered around two stable directions.
The magnetic field generated from these sources is corrupted by both low and high-frequency noise.
The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.

@@

\subsection{Applicability to more complex scenarios}

This test represents a more complex scenario by simulating typical grain distributions found in speleothem datasets.
The model is comprised of 103 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$.
The synthetic $b_z$ data were generated on a regular grid with $\qty{2}{\um}$ spacing and $\qty{5}{\um}$ sensor-sample distance.
We contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and $\qty{50}{\nano\tesla}$ standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.

@@

In order to assess the algorithm's ability to work with samples featuring higher concentrations of particles, we conducted a test of our algorithm on multiple synthetic datasets with increasing concentrations of randomly distributed magnetic grains in a volume of $2000 \times 2000 \times \qty{20}{\um}$. For each concentration, we generated 15 different random grain distributions. Figure~\ref{grain-concentration}a depicts the percentage of particles detected by the algorithm, with the median of the distribution represented by the red line. The same figure also presents the percentage of particles whose inversion results meet the filtering criteria of $R^2 \geq 0.85$ and $\text{SNR} \geq 5$, with the median represented by the blue line. As the number of particles increases, there is a consistent decrease in the percentage of sources detected. This is expected because of the spatial constraints of the algorithm, which require magnetic sources to be spatially separated for the detection algorithm to identify them. As shown in Figure~\ref{grain-concentration}b, by calculating the angular misfit between the vector sum direction of the model and the vector sum direction of the detected windows, it is observed that, for the unfiltered windows (red line), the angular misfits tend to increase with the concentration of magnetic grains. Nonetheless, this angular misfit tends to approach zero when the filtering criteria are applied, regardless of the particle concentration.

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/grain_concentration.png}
  \caption{
  Different grain simulations were randomly replicated (N=15) to assess the effectiveness of the algorithm to detect the magnetic sources. a) The efficacy of the detection was measured by the percentage of sources identified ($100 \left( N_{detected} ~/~ N_{true} \right)$) and showed as box-plots for both unfiltered detection (median represented as the red line) and filtered detection ($R^2 \geq 0.85$ and $SNR \geq 5$, blue line). b) The same representation is displayed for the angular misfit between the true vector sum and both results for the filtered and unfiltered sum of vectors detected. The blue/red dots represent outliers in the distributions.
  }
  \label{grain-concentration}
\end{figure}

@@

We developed an efficient semi-automated method to determine the position and dipole moments of dipolar sources on a microscale.
The method is an advancement towards the application of magnetic microscopy to paleomagnetic studies using thin sections.
A possible application is the isolation of the responses of more reliable recorders of the Earth's geomagnetic field from those of less reliable ones.

We also present a new way to solve the Euler deconvolution problem for determining the position of magnetic anomaly sources. Instead of the traditional moving window approach, we select data windows based on the Laplacian of Gaussian method applied to total gradient amplitude maps.
In this way, each window will ideally contain a single source and we are able to reduce the usually numerous spurious solutions to just a single solution per source.
This approach could also be adapted for traditional aeromagnetic data studies in cases where the sources are approximately spherical or only slightly elongated.
The source detection method is able to correctly isolate sources that are at
least \qty{15}{\um} apart for a source-sensor separation of \qty{5}{\um}.
For grain concentrations of 6250 grains/mm³, our method is
able to detect over 60\% of the particles present in the data.

@@

The test using a simple synthetic sample shows the capability of the method by estimating not only the precise center positions but also retrieving the magnetization directions and intensity for both dipolar and non-dipolar sources, even under the effect of high-frequency noise.
The test on a more complex synthetic sample highlights the applicability of the method in datasets resembling those obtained from speleothems.
The data are more complex with varied magnetization directions and intensity, in addition to also taking into account the high and low-frequency noise and sources with variable dipole moment intensities and depths.
The application to a real speleothem dataset positively answered the question of the algorithm's ability to deal with the real-world signals and noise.
It also showed the capacity of retrieving different magnetization directions recorded by magnetic minerals with different coercivities and magnetic signal intensity disparities.
We also assessed the quality of the fit between the predicted dipole model and the original magnetic data using two criteria: the coefficient of determination ($R^2$) and the signal-to-noise ratio (SNR).

We expect that this method can be widely applied to magnetic microscopy studies involving particles in the SD and PSD domains, particularly where grain concentrations are at or below 6000-10000 grains/mm³. The method can be applied in full as presented here or its individual components (source detection, Euler deconvolution, dipole moment inversion) can be combined with existing or future methods. There are still issues to be overcome with regard to situations where the signal of two or more sources overlap significantly, when non-dipolar effects are strong even at larger source-sensor separations, and how to best combine and benchmark the inversion results against microCT and micromagnetic modeling studies.
